### 2015-02-14 fundamentals/impl.tex
no more the the
using gls package

Dynamic Resource Exchange (DRE) is the critical resource-related process on
which \Cyclus simulations are built. It defines the resource interaction
mechanisms and methodologies for all agents. As the \Cyclus supply-demand
resolution framework, the DRE must be able to support arbitrary
facilities. Supporting the general \Cyclus philosophy, facilities are treated as
black boxes and a clear supply-demand communication framework is defined.

The DRE consists of three steps: supply-demand information gathering, resource
exchange solution, and trade execution. Importantly, each step is agnostic with
respect to the exchange of resources in question, i.e., the same procedure is
used for both Materials and Products. The information-gathering step consists of
three phases. First, consumers of commodities denote both the quantity of a
commodity they need to consume as well as the target isotopics, or quality, by
posting their demand to the market exchange as a series of \textit{requests}. An
optional collection of demand constraints are associated with each collection of
requests. Collections of requests may be grouped together, denoting
\textit{mutual} requests that represent demand for some common purpose. For
example, a reactor may request UOX and MOX fuel mutually, indicating that either
will satisfy its demand for fuel. Suppliers then respond to the series of
requests with a \textit{bid}. A bid supplies a notion of the quantity and
quality of a resource to match a request. Suppliers may add an arbitrary number
of constraints to accompany bids. For example, an enriched UOX supplier may
supply both a natural Uranium and SWU constraint. Any potential resource
transfer may be denoted as \textit{exclusive}. An exclusive transfer must either
be met fully or not at all in order to support concepts such as the the trading
of individual reactor assemblies. Finally, requesting facilities, institutions
and regions may apply \textit{preferences} to each potential request-bid pairing
based on the proposed resource transfer. Therefore, an institution can apply a
higher preference to a partner to which it is congenial; similarly, a region may
negate any transfers of material which have a higher Uranium enrichment than is
allowable.

The DRE may be solved either optimally by a mathematical program or
approximately by a simulation-based heuristic \TODO{cite}. If any trade is
denoted as exclusive, e.g., if an analyst desires an assembly-fidelity model,
then either a heuristic must be used or exchanges must be represented as
Mixed-Integer Nonlinear Programs (MILP). If no exclusive trades exist, a Linear
Programming (LP) model may be used. In practice, LPs solve much faster than
MILPs. However, the capability to model both exists in \Cyclus in order to
provide users with the desired level of fidelity.

Trades are initiated by the \Cyclus kernel after a solution to the DRE is
found. The DRE is executed at each time step. Therefore, if a facility's request
for a resource is not met at a given time step, it may offer a request in the
proceeding time step.

>>>>

The \gls{DRE} is the critical resource-related process on which \Cyclus
simulations are built. It defines the resource interaction mechanisms and
methodologies for all agents. As the \Cyclus supply-demand resolution framework,
the DRE must be able to support arbitrary facilities. Supporting the general
\Cyclus philosophy, facilities are treated as black boxes and a clear
supply-demand communication framework is defined.

The \gls{DRE} consists of three steps: supply-demand information gathering,
resource exchange solution, and trade execution. Importantly, each step is
agnostic with respect to the exchange of resources in question, i.e., the same
procedure is used for both Materials and Products. The information-gathering
step consists of three phases. First, consumers of commodities denote both the
quantity of a commodity they need to consume as well as the target isotopics, or
quality, by posting their demand to the market exchange as a series of
\textit{requests}. An optional collection of demand constraints are associated
with each collection of requests. Collections of requests may be grouped
together, denoting \textit{mutual} requests that represent demand for some
common purpose. For example, a reactor may request UOX and MOX fuel mutually,
indicating that either will satisfy its demand for fuel. Suppliers then respond
to the series of requests with a \textit{bid}. A bid supplies a notion of the
quantity and quality of a resource to match a request. Suppliers may add an
arbitrary number of constraints to accompany bids. For example, an enriched UOX
supplier may supply both a natural Uranium and SWU constraint. Any potential
resource transfer may be denoted as \textit{exclusive}. An exclusive transfer
must either be met fully or not at all in order to support concepts such as the
trading of individual reactor assemblies. Finally, requesting facilities,
institutions and regions may apply \textit{preferences} to each potential
request-bid pairing based on the proposed resource transfer. Therefore, an
institution can apply a higher preference to a partner to which it is congenial;
similarly, a region may negate any transfers of material which have a higher
Uranium enrichment than is allowable.

The \gls{DRE} may be solved either optimally by a mathematical program or
approximately by a simulation-based heuristic \TODO{cite}. If any trade is
denoted as exclusive, e.g., if an analyst desires an assembly-fidelity model,
then either a heuristic must be used or exchanges must be represented as a
\gls{MILP}. If no exclusive trades exist, a \gls{LP} model may be used. In
practice, LPs solve much faster than \gls{MILP}s. However, the capability to
model both exists in \Cyclus in order to provide users with the desired level of
fidelity.

Trades are initiated by the \Cyclus kernel after a solution to the \gls{DRE} is
found. The \gls{DRE} is executed at each time step. Therefore, if a facility's
request for a resource is not met at a given time step, it may offer a request
in the proceeding time step.
